MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
Every young computer scientist learns early in their career that all
data regardless of its meaning are all the same in their underlying
representation - simple ones and zeroes.
 It is only in the act of
reading and subsequently interpreting those data that computer
scientists or their creations give meaning to the bits and bytes.
MapReduce to My Ears is an exercise in the reinterpretation of data
meant to be understood as color and picture into sound and music.
Our method uses Hadoop, an open source implementation of the MapReduce
programming paradigm, to process a large corpus of images and extract
a musical representation.
 We have produce a six minutes and
thirty-five second audio/visual entitled \emph{Digital Nightmare}, the
style of which can be described as 8-bit, blast beat.
\end{abstract}
